Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-25 analysis/paper/paper.Rmd
Move model files to inst/extdata

load(file = here("data/m1.Rda"))
load(file = here("data/m2.Rda"))
load(file = here("data/m3.Rda"))
load(file = here("data/m4.Rda"))
load(file = here("data/m5.Rda"))
load(file = here("data/m6.Rda"))

>>>>

load(file = here("inst/extdata/m1.Rda"))
load(file = here("inst/extdata/m2.Rda"))
load(file = here("inst/extdata/m3.Rda"))
load(file = here("inst/extdata/m4.Rda"))
load(file = here("inst/extdata/m5.Rda"))
load(file = here("inst/extdata/m6.Rda"))
